Methods_tidy

### 2019-01-25 Methods_tidy.Rmd
updated

ggplot(data = SACTN_3yr, aes(x = date, y = insitu_temp, colour = site)) +
geom_line(aes(group = site)) +
labs(x = "", y = "Temperature (°C)") +
theme(axis.text.x = element_text(angle = 45)) +
theme_linedraw() +
theme(legend.position = "top")
```

@@

MUR_plot <- match_plot(df = insitu_MUR)
ggplot(data = insitu_MUR, aes(x = date, y = temp, colour = site)) +
geom_line(aes(group = site)) +
labs(x = "", y = "Temperature (°C)") +
theme(axis.text.x = element_text(angle = 45)) +
theme_linedraw() +
theme(legend.position = "top")
```

@@

# save(OISST_sites, file = "Data/OISST_sites.RData")
# load("~/Documents/MastersProject/Data/OISST_sites.RData")

OISST_sites <- OISST_sites %>% 
  dplyr::rename(temp = temp_OISST) %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  drop_na()
```

@@

ggplot(data = insitu_OISST, aes(x = date, y = temp, colour = site)) +
geom_line(aes(group = site)) +
labs(x = "", y = "Temperature (°C)") +
theme(axis.text.x = element_text(angle = 45)) +
theme_linedraw() +
theme(legend.position = "top")
```

@@

ggplot(data = insitu_G1SST, aes(x = date, y = temp, colour = site)) +
geom_line(aes(group = site)) +
labs(x = "", y = "Temperature (°C)") +
theme(axis.text.x = element_text(angle = 45)) +
theme_linedraw() +
theme(legend.position = "top")
```

>>>>

insitu_temp_plot <- ggplot(data = SACTN_3yr, aes(x = date, y = insitu_temp, colour = site)) +
geom_line(aes(group = site)) +
labs(x = "", y = "Temperature (°C)") +
theme(axis.text.x = element_text(angle = 45)) +
#theme_linedraw() +
theme(legend.position = "top")

# ggsave(plot = insitu_temp_plot, filename = "Figures/insitu_temp.pdf")
```

@@

MUR_plot <- match_plot(df = insitu_MUR)
mur_temp_plot <- ggplot(data = insitu_MUR, aes(x = date, y = temp, colour = site)) +
geom_line(aes(group = site)) +
labs(x = "", y = "Temperature (°C)") +
theme(axis.text.x = element_text(angle = 45)) +
#theme_linedraw() +
theme(legend.position = "top")

# ggsave(plot = mur_temp_plot, filename = "Figures/mur_temp_plot.pdf")

```

@@

# save(OISST_sites, file = "Data/OISST_sites.RData")
# load("~/Documents/MastersProject/Data/OISST_sites.RData")
load("~/Documents/Masters_2019/MastersProject/Data/OISST_sites.RData")
OISST_sites <- OISST_sites %>% 
  dplyr::rename(temp = temp_OISST) %>%
  dplyr::mutate(date = as.Date(date)) %>% 
  drop_na()
```

@@

OISST_temp_plot <- ggplot(data = insitu_OISST, aes(x = date, y = temp, colour = site)) +
geom_line(aes(group = site)) +
labs(x = "", y = "Temperature (°C)") +
theme(axis.text.x = element_text(angle = 45)) +
# theme_linedraw() +
theme(legend.position = "top")
# ggsave(plot = OISST_temp_plot, filename = "Figures/OISST_temp_plot.pdf")
```

@@

G1SST_temp_plot <- ggplot(data = insitu_G1SST, aes(x = date, y = temp, colour = site)) +
geom_line(aes(group = site)) +
labs(x = "", y = "Temperature (°C)") +
theme(axis.text.x = element_text(angle = 45)) +
# theme_linedraw() +
theme(legend.position = "top")
# ggsave(plot = G1SST_temp_plot, filename = "Figures/G1SST_temp_plot.pdf")
```
